---
title       : The great inventions and discoveries
subtitle    : a tale told by data
author      : data2knowledge
job         : the student on coursera
framework   : io2012   # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The great inventions and scientific discoveries

### The Goal 

The aim of this presentation is to present the Shiny application created for the course project of the Creating Data Products course in the Data Science Specialization.

### Synopsis

The great inventions and scientific discoveries explorer is based on the data of Yearly Numbers of Important Discoveries from Datasets package.

--- . Calss #id

### Data Processing

```{r}
library(datasets)
data(discoveries)
str(discoveries)
```

**discoveries** data set is the numbers of great inventions and scientific discoveries in each year from 1860 to 1959. 

### Ref:
For more information for datasetst,  click the URI below.  
(http://vincentarelbundock.github.io/Rdatasets/doc/datasets/discoveries.html)

--- . Calss #id
### The great inventions and scientific discoveries explorer
```{r fig.width=13, fig.height=6,echo=FALSE}
library(png)
library(grid)
img <- readPNG("discoveries.png")
grid.raster(img)
```

To see the application, click the URI below.  
(https://data2knowledge.shinyapps.io/project/)


--- . Calss #id

### The best year of inventions and scientific discoveries

The maximum discoveries
```{r}
max(discoveries)
```


The minimum discoveries
```{r}
min(discoveries)
```

There were `r max(discoveries) ` discoveries in `r which(discoveries %in% max(discoveries))+1859` and it was the best year of inventions and scientific discoveries. And there was no discoveries in `r which(discoveries %in% min(discoveries))+1859 `.
